---
title: "DATA607_HW4"
author: "Gabriel Santos"
date: "`r Sys.Date()`"
output: html_document
---

```{r readdb}
majorDS <- read.csv(file="https://raw.githubusercontent.com/fivethirtyeight/data/master/college-majors/majors-list.csv",header = TRUE, sep=",") 
```


#### *1.Using the 173 majors listed in fivethirtyeight.com’s College Majors dataset [https://fivethirtyeight.com/features/the-economic-guide-to-picking-a-college-major/], provide code that identifies the majors that contain either "DATA" or "STATISTICS"*


```{r E1}
key='DATA|STATISTICS'
majorDnS <- majorDS$Major[grep(key, majorDS$Major)]
majorDnS
```


#### *2.Write code that transforms the data below:*


[1] "bell pepper"  "bilberry"     "blackberry"   "blood orange"
[5] "blueberry"    "cantaloupe"   "chili pepper" "cloudberry"  
[9] "elderberry"   "lime"         "lychee"       "mulberry"    
[13] "olive"        "salal berry"
Into a format like this:
c("bell pepper", "bilberry", "blackberry", "blood orange", "blueberry", "cantaloupe", "chili pepper", "cloudberry", "elderberry", "lime", "lychee", "mulberry", "olive", "salal berry")
Using the 173 majors listed in fivethirtyeight.com’s College Majors dataset [https://fivethirtyeight.com/features/the-economic-guide-to-picking-a-college-major/], provide code that identifies the majors that contain either "DATA" or "STATISTICS"

```{r E2}
fruitDF <- data.frame(c("bell pepper", "bilberry", "blackberry", "blood orange", "blueberry", "cantaloupe", "chili pepper", "cloudberry", "elderberry", "lime", "lychee", "mulberry", "olive", "salal berry"))
cat(paste(fruitDF), collapse=",")
```


#### *3.Describe, in words, what these expressions will match:*


* (.)\1\1
* "(.)(.)\\\2\\\1"
* (..)\1
* "(.).\\\1.\\\1"
* "(.)(.)(.).*\\\3\\\2\\\1"
    

  + Any 3 same characters that next to each other.
  + Matching any 2 character and they in reverse order. 
  + Repeat any 2 characters. 
  + Any character 3 times and must be separated by one character. 
  + Matching any 3 character and they in reverse order.


```{r E3 }
library("stringr")
exampleDS <-c("lool", "aa", "aaa", "aaaa", "is is", "aa", "lolol", "abccba", "abcddcba", "aaaalaaa", "aaaaaal", "aaaaaa", "abccab", "abb", "aba", "awww")
#(.)\1\1"
expression ="(.)\\1\\1"
result <- str_subset(exampleDS,expression)
result
#"(.)(.)\\2\\1"
expression ="(.)(.)\\2\\1"
result <- str_subset(exampleDS,expression )
result
#"(..)\1"
expression ="(..)\\1"
result <- str_subset(exampleDS,expression )
result
#(.).\\1.\\1"
expression ="(.).\\1.\\1"
result <- str_subset(exampleDS,expression )
result
#"(.)(.)(.).*\\3\\2\\1"
expression ="(.)(.)(.).*\\3\\2\\1"
result <- str_subset(exampleDS,expression )
result
```


#### *4. Construct regular expressions to match words that:*


  - Start and end with the same character.
  - Contain a repeated pair of letters (e.g. "church" contains "ch" repeated twice.)
  - Contain one letter repeated in at least three places (e.g. "eleven" contains three "e"s.)

```{r E4 }
sampleDS <-c("eye", "dad", "mom", "prep", "lateral", "pulp", "pop", "madam", "treat", "tent", "essence", "nose", "stress" , "high" , "tall", "call", "zeus", "church", "chicken", "chocolate", "banana", "lululemon")
#Start and end with the same character.
expression ="^(.)(.*\\1$)"
result <- str_subset(sampleDS,expression )
result
#Contain a repeated pair of letters (e.g. "church" contains "ch" repeated twice.)
expression="([A-Za-z][A-Za-z]).*\\1"
result <- str_subset(sampleDS,expression )
result
#Contain one letter repeated in at least three places (e.g. "eleven" contains three "e"s.)
expression="([A-Za-z]).*\\1.*\\1"
result <- str_subset(sampleDS,expression )
result
```